### 2008-03-21 trunk/Papers/dl-gre-08/bisim.tex
moved figures around

Below, we will use a key notion of formula preservation that we call
\emph{similarity}.  For any description logic $\gL$, we will say that
an individual $i$ is \emph{\gL-similar} to $i'$ in a given model $\gM$
if for any formula $\varphi \in \gL$ such that $i \in
\interp{\varphi}$, we also have $i' \in \interp{\varphi}$.
Equivalently, there is no $\gL$-formula that holds of $i$ but not of
$i'$.  We say that the \emph{\gL-similarity set} of some individual
$i$ is the set of all individuals to which $i$ is \gL-similar.

>>>>

Below, we will use a key notion of formula preservation that we call
\emph{similarity}.  For any DL $\gL$, we will say that
an individual $i$ is \emph{\gL-similar} to $i'$ in a given model $\gM$
if for any formula $\varphi \in \gL$ such that $i \in
\interp{\varphi}$, we also have $i' \in \interp{\varphi}$.
Equivalently, there is no $\gL$-formula that holds of $i$ but not of
$i'$.  We say that the \emph{\gL-similarity set} of some individual
$i$ is the set of all individuals to which $i$ is \gL-similar.

### 2008-03-21 trunk/Papers/dl-gre-08/gre.tex
moved figures around

It can be shown that for \alc, the similarity sets of a finite model
coincide exactly with the \emph{simulation classes} of this model.
Simulation classes have been studied extensively in the literature
\cite{blac:moda01,kurt:expr99}, and there are several efficient
algorithms for computing \alc-simulation classes
\cite{hopc:algo71,paig:thre87,dovier04:_effic_algor_for_comput_bisim_equiv}.
However, these algorithms will only compute the simulation classes
themselves. Here we extend the \newcite{hopc:algo71} algorithm such
that it computes, along with each set, also a formula that denotes
exactly this set.  We can then use these formulas as representations
of the REs.

>>>>

It can be shown that for \alc, the similarity sets of a finite model
coincide exactly with the \emph{simulation classes} of this model.
Simulation classes have been studied extensively in the literature
(see e.g. \newcite{blac:moda01}; \newcite{kurt:expr99}), and there are several
efficient algorithms for computing \alc-simulation classes
\cite{hopc:algo71,paig:thre87,dovier04:_effic_algor_for_comput_bisim_equiv}.
However, these algorithms will only compute the simulation classes
themselves. Here we extend the \newcite{hopc:algo71} algorithm such
that it computes, along with each set, also a formula that denotes
exactly this set.  We can then use these formulas as representations
of the referring expressions.
